Mitigating (D)DoS in Named-Data Networking

### 2012-10-23 algos/dynamic-limits.tex
Adding fair-queueing algorithm description
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@815 df1a90cd-247b-4364-bdaf-287a704eb499
Adding draft for dynamic limits algorithm
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@816 df1a90cd-247b-4364-bdaf-287a704eb499

\subsection{Dynamic limits assignment algorithm}

>>>>

\subsection{Dynamic limits assignment algorithm}
\label{sec:dynamic limits}

A notable problem of the queuing method is that the method tries to differentiate between good and malicious Interests, but does not effectively limit the amount of malicious Interests.
That is, if an attacker has a large number of malicious Interests to send, it will receive a slightly lower priority in sending these Interests (some will be delayed more, some number will be dropped), but a lot of these Interests will get through.
To solve this problem, we propose announcing and dynamically readjusting Interest limits for classes (e.g., per prefix and per incoming face), based on Interest satisfaction ratios for those classes. 
Pseudocode~\ref{alg:dynamic limits} summarizes our proposal, which is a variation of a well-known push-back mechanism.

\floatname{algorithm}{Pseudocode}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{algorithm}[h]
\caption{Dynamic limits}
\label{alg:dynamic limits}
\begin{algorithmic}[1]
\Function{InInterest}{Interest $i$, InFace $if$}
\For{\textbf{each} OutFace $of$ \textbf{in} ForwardingDecision($i,if$)}
    \State $l \leftarrow of$.GetPerPrefixLimit($i$)
    \If{$l$ is under dynamics limits \textbf{and} $of$ is under physical limits}
        \State Forward($i$, $of$)
    \Else
        \State Drop or enqueue Interest $i$
    \EndIf
\EndFor
\EndFunction

\vspace{0.2cm}

\Function{AnnounceLimits}{} \Comment{\textit{E.g., every second}}
\For{\textbf{each} prefix $p$ in FIB}
    % \State{} \Comment{Get total limit for the prefix $p$}
    \State $L \leftarrow \displaystyle\sum\limits_{\mathrm{\forall \mathit{of} \in FIB(\mathit{p})}}{}{}of$.GetPerPrefixLimit($p$)
    \State $R \leftarrow 0$
    \For{\textbf{each} available face $f$}
        \State $l_f \leftarrow L \times p$.$f$.GetSatisfactionRatio()
        \State $R \leftarrow R + p$.$f$.GetSatisfactionRatio()
    \EndFor

    \If{$\displaystyle\sum\limits_{\forall f}^{}l_f < l$} \Comment{If under-utilization detected}
        \State $\forall f : l_f \leftarrow \displaystyle\frac{l_f}{R}$ \Comment{Normalize limits}
    \EndIf

        \State AnnounceLimit($f$, $p$, $l$)
\EndFor
\EndFunction

\vspace{0.2cm}

\State{} \Comment{\textit{When announcement from the neighbor is received}}
\Function{InLimits}{InFace $if$, Prefix $p$, Limit $l$}
    \State $if$.GetPerPrefixLimit($p$) $\leftarrow l$ 
\EndFunction

\end{algorithmic}
\end{algorithm}

When an Interest arrives, in addition to be checked against per-outgoing interface limits, it is subjected to per-prefix per-incoming interface limits (lines 3 and 4 in Pseudocode~\ref{alg:dynamic limits}).
In other words, for each prefix in FIB a node cannot send more Interests than a specified limit for this prefix (``dynamic limits''), as well as the node cannot send out more Interests out of the face, than the limit specified for this face (``physical limit'').
While the latter is defined in the same manner as in Section~\ref{sec:physical limits}, ``dynamic limits'' are periodically announced to all neighbors (\textit{AnnounceLimits} function) and adjusted based on received announcements from neighbors (\textit{InLimits} function).%
\footnote{The initial value (not specified in the pseudocode) for the dynamic limits is the corresponding physical limits.}

During the announcement phase, a node tries to determine ``quality'' of neighbors in terms of Interest satisfaction rations and tries to give more resources (accept more Interests from) neighbors with better satisfaction ratios.
At the same time, it is undesirable to over-limit neighbors when there are available resources.
That is, when the sum of all limits calculated by directly applying the satisfaction ratios to the total available limit (lines 15-18 in Pseudocode~\ref{alg:dynamic limits}), limits should be normalized so the sum of all announced limits is at least equal to the total available limit (lines 19-21).

When the satisfaction ratio for a particular prefix and incoming interface becomes close to zero, a node starts announcing (and in real implementation, enforcing) the zero limit.
The node will keep announcing this zero limit for a time period, depending on statistics degradation curve (see more in Section~\ref{sec:stats}).

The dynamic limits method can work as standalone algorithm, as well as it can be (and we believe that it should be, and all results presented in this paper are based on) coupled with the queuing algorithms.
This way, the dynamic limits part pushes back malicious traffic, while queueing part provides limited per-incoming interface fairness for good traffic.

### 2012-10-23 algos/fair-queueing.tex
Adding draft for dynamic limits algorithm
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@816 df1a90cd-247b-4364-bdaf-287a704eb499

One way of augmenting the physical limits method with data performance knowledge is to perform some sort of class-based Interest queueing and weighted scheduling (e.g., weighted round-robin) of the enqueued interests with the weight equal to the Interest satisfaction ratio for the class (see Algorithm~\ref{alg:queuing}).
For example, Interests can be divided into separate classes based on incoming interface, where Interests arriving from different incoming interfaces are treated differently:
an Interest from an interface with higher satisfaction ratio will have more priority than an Interest from an interface with lower satisfaction ratio.

@@

While we experimented with more complicated classes (see Sections~\ref{sec:dynamic limits} and \ref{sec:probabilistic model}), limitations of the queuing method nullify benefits of implementing such classes.
In particular, weighted round-robin scheduling can effectively work only if queues are not empty.
But, as we evaluation results in Section~\ref{sec:evaluation} show, queues are tend to be empty, when number of bottlenecks (mixing points, nodes that receive more Interests that they can forward on a face) on paths more than one.

>>>>

One way of augmenting the physical limits method with data performance knowledge is to perform some sort of class-based Interest queueing and weighted scheduling (e.g., weighted round-robin) of the enqueued interests with the weight equal to the Interest satisfaction ratio for the class (see Pseudocode~\ref{alg:queuing}).
For example, Interests can be divided into separate classes based on incoming interface, where Interests arriving from different incoming interfaces are treated differently:
an Interest from an interface with higher satisfaction ratio will have more priority than an Interest from an interface with lower satisfaction ratio.

@@

While we experimented with more complicated classes (see Sections~\ref{sec:dynamic limits} and \ref{sec:probabilistic}), limitations of the queuing method nullify benefits of implementing such classes.
In particular, weighted round-robin scheduling can effectively work only if queues are not empty.
But, as we evaluation results in Section~\ref{sec:evaluation} show, queues are tend to be empty, when number of bottlenecks (mixing points, nodes that receive more Interests that they can forward on a face) on paths more than one.

### 2012-10-23 algos/probabilistic.tex
Adding draft for dynamic limits algorithm
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@816 df1a90cd-247b-4364-bdaf-287a704eb499

\documentclass[conference]{IEEEtran}
\title{Mitigating (D)DoS in Named-Data Networking}%:\\ Cache/Content Poisoning}
\author{anonymous}

\usepackage{graphicx}
% \usepackage[colorlinks]{hyperref}
\usepackage[]{hyperref}
\usepackage{breakurl}
\usepackage{url}
\usepackage[nocompress]{cite}
% \usepackage{verbatim}
% \usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{algpseudocode}

\begin{document}
\maketitle

\begin{abstract}
%
abstract
%
\end{abstract}

\noindent {\bf Keywords:} Future Internet Architectures;
Content-Centric Networks; Information-Centric Networks, Named-data
Networking; Security; Denial-of-Service; Distributed
Denial-of-Service.

\section{Introduction \label{intro}}
Current Internet architecture and its resilience to DoS and DDOS. Requirements from a new architecture such as CCN with respect to DoS and DDoS resilience.

Our contributions.

Paper organization.

\section{ CCN Overview\label{ccn-intro}}

\section { DDoS Attacks in CCN \label{ccn-ddos}}
Brief overview of possible attacks in CCN, and scope of what we will tackle in this paper (Interest flooding).

\section { Interest Flooding in CCN }

\section {Countermeasures against Interest flooding}

Basic limits, probablity based on statistics, and dynamic window adjustment

(Description of each of the above, and their implications)

\section {Evaluation}
 Both simulation, as well as emulation for various sized topologies (trees as well as real topologies), various parameters etc.
List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.

Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers, Latency for good clients, good versus bad interests as a function of time).

\subsection{Simulation versus Emulation}
Results establishing validity of  simulator.

\subsection{Results from probability based on statistics}

\subsection{Results from dynamic window adjustment}

\section{Implications/Analysis}
Lessons we learnt, comparison of different mitigation techniques. 
Adapting these to mitigate other DDoS attacks.

\section{Conclusions and Future Work}

\bibliographystyle{plain}
\bibliography{references}

\appendix

\input{algos/physical-limits.tex}

\input{algos/fair-queueing.tex}

\input{algos/stats.tex}

\input{algos/dynamic-limits.tex}

\subsection{Probabilistic Interest accept algorithm}

\end{document}

>>>>

\subsection{Probabilistic Interest accept algorithm}
\label{sec:probabilistic}
